Output Summary

### 2021-08-31 03-post-process/output-plots.Rmd
Include data uncertainty in abundance fit plots

```{r fall-trap-N-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^Pa[.+,LH_type,pop]$", LH_type = i_fall, pop = j)), jags_data$Pa_obs[observable,i_fall,j], main = pops[j])
}

@@

```{r spring-trap-N-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^Mb[.+,LH_type,origin,pop]$", origin = o_nor, LH_type = i_spring, pop = j)), jags_data$Mb_obs[observable,i_spring,o_nor,j], main = pops[j])
}

@@

```{r adult-N-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^Ra_tot[.+,pop]$", pop = j)), jags_data$Ra_obs[observable,j], main = pops[j])
}

>>>>

```{r fall-trap-N-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^Pa[.+,LH_type,pop]$", LH_type = i_fall, pop = j)),
               get_obs_ests_log_normal(log(jags_data$Pa_obs[observable,i_fall,j]), jags_data$sig_Pa_obs[observable,i_fall,j]),
               main = pops[j])
}

@@

```{r spring-trap-N-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^Mb[.+,LH_type,origin,pop]$", origin = o_nor, LH_type = i_spring, pop = j)), 
               get_obs_ests_log_normal(log(jags_data$Mb_obs[observable,i_spring,o_nor,j]), jags_data$sig_Mb_obs[observable,i_spring,o_nor,j]),
               main = pops[j])
}

@@

```{r adult-N-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^Ra_tot[.+,pop]$", pop = j)),
               get_obs_ests_log_normal(log(jags_data$Ra_obs[observable,j]), jags_data$sig_Ra_obs[observable,j]),
               main = pops[j])
}
